The Surprising Runtime Fragility Found when Querying a Single Table

### 2015-04-13 testdata/chunked_column_layouts/draft.tex
!

\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{testtest, dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}
\renewcommand\pdbfScale{1.00}
\renewcommand\pdbfQuality{1.00}

>>>>

\DBSQLFile{somedb.sql}
\DBSQLJDBC{jdbc:postgresql://localhost:5432/postgres}{postgres}{test}{dim_time, dim_compiler, dim_dataset, dim_implementation, dim_layout, dim_query, dim_machine, fact_experiment}
\renewcommand\pdbfScale{1.00}
\renewcommand\pdbfQuality{4.00}
